Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
finished AUG shotplan 	modified:   gpm_november2016_vianello.tex

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{H-mode experiments}
\begin{itemize}
	\item ITER and DEMO will operate in H-mode
	\item We must know what parameters control shoulder formation 
	\item Shoulder formation parameter regime is unclear on all machines
	\item Main priorities: 
	\begin{enumerate}
		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
		\item Experiments must gradually increase power and density. 
	\end{enumerate}
\end{itemize}

@@

\begin{frame}{Required diagnostics}
In order to compare experiments the following diagnostics must be available: 
\begin{enumerate}
	\item Reciprocating probe at OM measuring: 
	\begin{itemize} 
		\item $I_sat$ on minimum three pins poloidally and radially separated
		 (filamens speed and size). 
		\item Electron temperature
		\item If possible $M_{\|}$
	 \end{itemize}
	 \item Camera viewing OM for measuring neutrals 
	 \item Divertor measurements of $n$ and $T_e$ (probes). Collisionallity
	 \item Density profile measurements (Li-Bes, Reflectometry, Edge Thomson scattering) 
%	\item H-mode quality diagnostics(div current, magnetics)
\end{enumerate}
\end{frame}

\begin{frame}{Proposed shot plan - AUG}
Allocated shots $\sim$ 14 + contingency 
\begin{itemize}
	\item L-Mode (6 shots)
	\begin{enumerate}
		\item 
	\end{enumerate}
\end{itemize}

Choose fueling levels for reference shot at 0.8 MA from AUG14-2.2-3 30276. Perform the same density ramp at 0.6 MA by keeping the same Toroidal Field
Repeat Shot  1 by keeping the same q95 as reference
Repeat Shot  30276 @ 1MA with the same toroidal field
Repeat  3 by keeping the same q95 as the reference
Repeat  30276 with Reverse Bt
Repeat  5 with Probe at different insertion
H-Mode investigation: Foreseen number 9

The reference shot is 33059 (AUG15-2.2-3) with the aim to reach the condition found in 31607 (Sun PPCF 2015)

Scenario development. Start from succesful shot 33059 (Total heating 3.1 MW), keep the probe head in a safe position (FAR SOL) increase the heating power (two steps to 4.5 and 6) up to 6 MW monitoring midplane probe by IR and Divertor through Langmuir.
Repeat  1 Fueling ramps according to reference. Monitor of Divertor condition
Repeat  2 adjusting eventually the fueling and N seeding ramp monitoring the Divertor condition
Repeat  4 with optimum level of Fueling/Seeding 1st Radial position of probe
Repeat  5, different probe position
Repeat  6, different probe position
Repeat  6 with Strike-point sweeping (if feasible)
Contingency
Contingency

	piggybaggers (Mclements, relfectometry guys)

	COMPASS
\end{frame}

@@

>>>>

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
		\item Reaching all goals is not possible with the current number of allocated shots.
	\end{itemize}
\end{frame}

@@

\begin{frame}{H-mode experiments}
\begin{itemize}
	\item ITER and DEMO will operate in H-mode
	\item We must know what parameters control shoulder formation 
	\item Shoulder formation parameter regime is unclear on all machines
	\item Main priorities: 
	\begin{enumerate}
		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
		\item Experiments must gradually increase power and density. 
	\end{enumerate}
	\item Fueling in H-mode is problematic due to transport barrier? 
\end{itemize}

@@

\begin{frame}{Required diagnostics}
In order to compare experiments the following diagnostics must be available: 
\begin{enumerate}
	\item Reciprocating probe at OM measuring: 
	\begin{itemize} 
		\item $I_{sat}$  on minimum three pins poloidally and radially separated
		 (filamens speed and size). 
		\item Electron temperature
		\item If possible $M_{\|}$
	 \end{itemize}
	 \item Camera viewing OM for measuring neutrals 
	 \item Divertor measurements of $n$ and $T_e$ (probes). Collisionallity
	 \item Density profile measurements (Li-Bes, Reflectometry, Edge Thomson scattering) 
%	\item H-mode quality diagnostics(div current, magnetics)
\end{enumerate}
\end{frame}

\begin{frame}{Proposed shot plan - AUG}
\vspace{-1cm}
Allocated shots $\sim$ 14 + contingency 
\begin{itemize}
	\item L-Mode (6 shots)
	\begin{enumerate}
		\item Reference shot \# 30276
		\item Perform $I_p$ scan (three values) with fixed $B_T$
		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello

	\end{enumerate}
	\item H-mode (9 shots)
	\begin{enumerate}
		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
		\item Strike-point sweep if feasible? 
		\item In all shots, particle acceleration in ELMs will be studied using microwaves, soft X-rays, and FILD (proposal by McClements) 
		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
		\item These shots combine experiments proposed by: Aguiam, Carralero, McClements, Militello, Vianello, Vicente

	\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Proposed shot plan - TCV}

\begin{frame}{With aloocated shot we cannot do interesting stuff }
\begin{itemize}
	\item Ion temp measurements
	\item Topology investigations
	\item Strikepoint sweeping and cryo pump
	\item Parameters scans in H-mode
	\item Strike-point sweep

\end{itemize}
\end{frame}

\begin{frame}{piggybag on Quescient H-mode shots}
\end{frame}

@@

	Form experiment planning groups for each machine
